PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-24 paper/sec-pineappl.tex
Shift the section 'Perturbative orders' to the end

\subsubsection{Perturbative orders}

%\subsubsection{Example: top-pair production}
%
%\begin{equation}
%\begin{split}
%\sigma_{ab}
%&= \alpha^2                                                                       W_{ab}^{(0,2,0,0)}
% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(1,1,0,0)}
% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(2,0,0,0)} \\
%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)                                  W_{ab}^{(3,0,0,0)} \\
%&+ \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{F}^2) W_{ab}^{(3,0,0,1)} (Q^2)
% + \alphas^3 \left( \xi_\mathrm{R}^2 Q^2 \right)          \log (\xi_\mathrm{R}^2) W_{ab}^{(3,0,1,0)} (Q^2) \\
%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha                           W_{ab}^{(2,1,0,0)} \\
%&+ \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{F}^2) W_{ab}^{(2,1,0,1)} (Q^2)
% + \alphas^2 \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha   \log (\xi_\mathrm{R}^2) W_{ab}^{(2,1,1,0)} (Q^2) \\
%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2                         W_{ab}^{(1,2,0,0)} \\
%&+ \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{F}^2) W_{ab}^{(1,2,0,1)} (Q^2)
% + \alphas   \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^2 \log (\xi_\mathrm{R}^2) W_{ab}^{(1,2,1,0)} (Q^2) \\
%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3                         W_{ab}^{(0,3,0,0)} \\
%&+           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{F}^2) W_{ab}^{(0,3,0,1)} (Q^2)
% +           \left( \xi_\mathrm{R}^2 Q^2 \right) \alpha^3 \log (\xi_\mathrm{R}^2) W_{ab}^{(0,3,1,0)} (Q^2)
%\end{split}
%\end{equation}

\subsection{Grid representations}
\label{sec:grid-representation}

@@

\subsubsection{4-tuples}

A straightforward representation is provided by  4-tuples, a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
For each combination $(a,b,k,l,m,n,o)$ (see section~\ref{sec:multi-coupling-expansion} for their definition) we save the following 4-tuples,
\begin{equation}
\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \mathcal{O}_i) \right\}_{i=1}^N \text{.} \label{eq:four-tuples}
\end{equation}
The reconstruction of the differential cross section is then done by simply multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, $o$, and $i$.

@@

\subsubsection{Lagrange-interpolation grid}

A different strategy is to partition the $(x_1, x_2, Q^2)$ space,
\begin{equation}
H = [x_\mathrm{min},x_\mathrm{max}]^2 \times [Q^2_\mathrm{min}, Q^2_\mathrm{max}] \ni (x_1, x_2, Q^2)
\end{equation}
along each axis into a small number of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
Using the bin centres and their values one already has a straightforward implementation of eq.~\eqref{eq:weight-map}, but given a finite number of bins usually yields an insufficient approximation for the cross section.
Increasing the number of bins improves the precision, but it also increases the space requirements.
Interpolation methods increase the precision using the same number of bins.

@@

>>>>

\subsubsection{Grid representations}
\label{sec:grid-representation}

@@

\paragraph{4-tuples}
A straightforward representation is given by 4-tuples, i.e.\ a list of the momentum fractions $x_1$ and $x_2$, the scale $Q^2$, and the phase-space weight $w$ for each phase-space point; 4-tuples are sufficient to reconstruct a total cross section.
For each combination $(a,b,k,l,m,n,o)$ (see section~\ref{sec:multi-coupling-expansion} for their definition) we save the following 4-tuples,
\begin{equation}
\left\{ x_1^i, x_2^i, Q^2_i, w^{(k,l,m,n,o)}_{ab} (x_1^i, x_2^i, Q^2_i, \mathcal{O}_i) \right\}_{i=1}^N \text{.} \label{eq:four-tuples}
\end{equation}
The reconstruction of the differential cross section is then done by simply multiplying the phase-space weights $w$ with PDFs evaluated with the correct arguments given in the 4-tuple and summing over all indices $a$, $b$, $k$, $l$, $m$, $n$, $o$, and $i$.

@@

\paragraph{Lagrange-interpolation grid}
A different strategy is to partition a subset $H$ of the $(x_1, x_2, Q^2)$ space,
\begin{equation}
H = [x_\mathrm{min},x_\mathrm{max}]^2 \times [Q^2_\mathrm{min}, Q^2_\mathrm{max}] \ni (x_1, x_2, Q^2)
\end{equation}
along each axis into a small number of bins and to insert the phase-space weights $w$ into the corresponding discrete bin.
Using the bin centres and their values one already has a straightforward implementation of eq.~\eqref{eq:weight-map}, but given a finite number of bins usually yields an insufficient approximation for the cross section.
Increasing the number of bins improves the precision, but it also increases the space requirements.
Interpolation methods increase the precision using the same number of bins.

@@

\subsection{Perturbative orders}
